Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-30 wearables_survey.tex
inserted some comments

@@

>>>>

SAY THIS: full on stats test on all 74 data types seems unreasonable. Look at the regression model below.

@@

SAY THIS: we performed an exploratory analysis to examine the effect of data recipient using a chi square test; in order to do this, the assumption about independence of observations was violated.However, we do not believe that this impacted the outcome of the statistical test based on the randomization of treatments across all conditions, as well as the very large sample size. To examine whether the violation of this assumption impacted our results, we further created a mixed effects model, in order to isolate the subjects variable (i.e., to examine the extent to which random effects stemming from individual differences may be responsible for the effects that we observed) !!!report effect sizes
